---
title: "TFM"
author: "Marta Ilundain Martínez" 
output:
  pdf_document: default
  html_document: default
heather-includes:
- \usepackage[english]{babel}
- \usepackage{amsmath}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \usepackage{float}
- \usepackage{booktabs}
- \fancyfoot[CO, CE]{\thepage}
- \fancyfoot[LE, RO]{Multivariant analysis, third exercise}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
bmatrix = function(x, digits=NULL, ...) {
  library(xtable)
  default_args = list(include.colnames=FALSE, only.contents=TRUE,
                      include.rownames=FALSE, hline.after=NULL, comment=FALSE,
                      print.results=FALSE)
  passed_args = list(...)
  calling_args = c(list(x=xtable(x, digits=digits)),
                   c(passed_args,
                     default_args[setdiff(names(default_args), names(passed_args))]))
  cat("\\begin{bmatrix}\n",
      do.call(print.xtable, calling_args),
      "\\end{bmatrix}\n")
}
```


# TFM

### Dataset


```{r include=FALSE}
set.seed(1998)
load("D:/Máster/Asignaturas/TFM/datos-calls.RData")
```

```{r include=FALSE} 
dat[,8] = dat[,8] + 6 
```

```{r include=FALSE}
# One hot encoding 
library(fastDummies)
dat = dummy_cols(dat,  select_columns = "wd")
dat = dat[,-c(15)]
colnames(dat)
colnames(dat)=c("type0","type1","type2","type3","wd","d","m","y",'Mon','Tue','Wed','Thu','Fri','Sat')
```

```{r include=FALSE}
library(readr)
library(Metrics)

weather <- read_csv("D:/Máster/Asignaturas/TFM/weather.csv")
weather = weather[,7]  
weather$prec = as.factor(weather$prec)
```


```{r include=FALSE}
weather$prec <- gsub("\\,", ".", weather$prec)
weather$prec = as.numeric(weather$prec)
weather[is.na(weather)] = 0 
```

```{r include=FALSE}
data = cbind(dat, weather)
rm(dat,weather)
str(data)
```

```{r}
data$Nt = rowSums(data[,1:4])
```




### Visualization of the data.


```{r include=FALSE}
# Total number of calls for each type
# total0 = sum(data$type0)
# total1 = sum(data$type1)
# total2 = sum(data$type2)
# total3 = sum(data$type3)

# Mean of the total number of calls per day for each type (for the 4079 observations) 
# mean0 = mean(data$type0)
# mean1 = mean(data$type1)
# mean2 = mean(data$type2)
# mean3 = mean(data$type3)

# Total number of calls 
# totalcalls = 87087+34116+8983+4520

# Total number of calls for each year
# calls2007 = sum(data$type0[data$y == 2007]) + sum(data$type1[data$y == 2007]) + sum(data$type2[data$y == 2007]) + sum(data$type3[data$y == 2007])
# calls2008 = sum(data$type0[data$y == 2008]) + sum(data$type1[data$y == 2008]) + sum(data$type2[data$y == 2008]) + sum(data$type3[data$y == 2008])
# calls2009 = sum(data$type0[data$y == 2009]) + sum(data$type1[data$y == 2009]) + sum(data$type2[data$y == 2009]) + sum(data$type3[data$y == 2009])
# calls2010 = sum(data$type0[data$y == 2010]) + sum(data$type1[data$y == 2010]) + sum(data$type2[data$y == 2010]) + sum(data$type3[data$y == 2010])
# calls2011 = sum(data$type0[data$y == 2011]) + sum(data$type1[data$y == 2011]) + sum(data$type2[data$y == 2011]) + sum(data$type3[data$y == 2011])
# calls2012 = sum(data$type0[data$y == 2012]) + sum(data$type1[data$y == 2012]) + sum(data$type2[data$y == 2012]) + sum(data$type3[data$y == 2012])
# calls2013 = sum(data$type0[data$y == 2013]) + sum(data$type1[data$y == 2013]) + sum(data$type2[data$y == 2013]) + sum(data$type3[data$y == 2013])
# calls2014 = sum(data$type0[data$y == 2014]) + sum(data$type1[data$y == 2014]) + sum(data$type2[data$y == 2014]) + sum(data$type3[data$y == 2014])
# calls2015 = sum(data$type0[data$y == 2015]) + sum(data$type1[data$y == 2015]) + sum(data$type2[data$y == 2015]) + sum(data$type3[data$y == 2015])
# calls2016 = sum(data$type0[data$y == 2016]) + sum(data$type1[data$y == 2016]) + sum(data$type2[data$y == 2016]) + sum(data$type3[data$y == 2016])
# calls2017 = sum(data$type0[data$y == 2017]) + sum(data$type1[data$y == 2017]) + sum(data$type2[data$y == 2017]) + sum(data$type3[data$y == 2017])
# calls2018 = sum(data$type0[data$y == 2018]) + sum(data$type1[data$y == 2018]) + sum(data$type2[data$y == 2018]) + sum(data$type3[data$y == 2018])

# Plot of the evolution of number of calls
# yearcall = cbind(calls2007,calls2008, calls2009, calls2010, calls2011, calls2012, calls2013, calls2014, calls2015, calls2016, calls2017, calls2018)
# year = c(2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018)
# hist(yearcall)
# plot(year, yearcall)
# 
# # Rate of total calls for each type
# rate0 = 87087/4079
# rate1 = 34116/4079
# rate2 = 8983/4079
# rate3 = 4520/4079

# par(mfrow=c(2,2))
# plot(data$wd,data$type0, col= rainbow(7))
# plot(data$wd,data$type1, col= rainbow(7))
# plot(data$wd,data$type2, col= rainbow(7))
# plot(data$wd,data$type3, col= rainbow(7))
# 
# # install.packages("RColorBrewer")
# library(RColorBrewer)
# # display.brewer.all()
# 
# plot(data$wd,data$Nt, col= brewer.pal(n = 7, name = "PuBu"),ylab="Total number of calls",xlab="Day of the week", main="Total calls for each type given Rain and Weekday")
```

```{r include=FALSE}
data$Rain = data$prec
data$Rain[data$Rain < 2]=0
data$Rain[data$Rain > 15 & data$Rain != "weak" & data$Rain != "normal" ]=1 
data$Rain[data$prec >=2 & data$prec <= 15]=1
```
 
```{r echo=FALSE, fig.align='center', message=FALSE, warning=FALSE, out.width='12.2cm'}
library(ggpubr)
library(ggplot2)
# plot1 = ggplot(data, aes(x=wd, y=type0, color=Rain)) +
#     geom_point(alpha=0.7) + theme_bw()+
#   guides(colour = "none")
# plot2 = ggplot(data, aes(x=wd, y=type1, color=Rain)) +
#     geom_point(alpha=0.7) + theme_bw()+
#   guides(colour = "none")
# plot3 = ggplot(data, aes(x=wd, y=type2, color=Rain)) +
#     geom_point(alpha=0.7) + theme_bw()+
#   guides(colour = "none")
# plot4 = ggplot(data, aes(x=wd, y=type3, color=Rain)) +
#     geom_point(alpha=0.7) + theme_bw()
# ggarrange(plot1,plot2,plot3,plot4)
# ggarrange(plot3,plot4)
```

```{r}
# plot1 = ggplot(data, aes(x=wd, y=type0, color=prec)) +
#     geom_point(alpha=0.7) + theme_bw()
# plot2 = ggplot(data, aes(x=wd, y=type1, color=prec)) +
#     geom_point(alpha=0.7) + theme_bw()
# plot3 = ggplot(data, aes(x=wd, y=type2, color=prec)) +
#     geom_point(alpha=0.7) + theme_bw()
# plot4 = ggplot(data, aes(x=wd, y=type3, color=prec)) +
#     geom_point(alpha=0.7) + theme_bw()
# ggarrange(plot1,plot2)
# ggarrange(plot3,plot4)
```


```{r include=FALSE}
# sum0_by_year <- aggregate(type0 ~ y, data = data, FUN = sum)
# sum1_by_year <- aggregate(type1 ~ y, data = data, FUN = sum)
# sum2_by_year <- aggregate(type2 ~ y, data = data, FUN = sum)
# sum3_by_year <- aggregate(type3 ~ y, data = data, FUN = sum)
```

```{r echo=FALSE, fig.align='center', message=FALSE, warning=FALSE, out.width='12.2cm'}
# plot5 = ggplot(sum0_by_year, aes(x = y, y = type0)) +
#     geom_bar(stat = 'identity', fill = "#4fa8e0")   + theme_bw() +
#     xlab("Year") + ggtitle("Total calls of type0 over the years")
# plot6 = ggplot(sum1_by_year, aes(x = y, y = type1 ))+
#     geom_bar(stat = 'identity', fill = "#6c8bab") + theme_bw() +
#     xlab("Year") + ggtitle("Total calls of type1 over the years")
# plot7 = ggplot(sum2_by_year, aes(x = y, y = type2 ))+
#     geom_bar(stat = 'identity', fill ="#72b7e3") + theme_bw() +
#     xlab("Year") + ggtitle("Total calls of type2 over the years")
# plot8 = ggplot(sum3_by_year, aes(x = y, y = type3 ))+
#     geom_bar(stat = 'identity', fill = "#597d94") + theme_bw() +
#     xlab("Year") + ggtitle("Total calls of type3 over the years")
# 
# ggarrange(plot5,plot6)
# ggarrange(plot7,plot8)
```

```{r}
# PROPORTION FOR ALL THE YEAR
# prop0 = sum(data$type0)/sum(data$Nt)
# prop1 = sum(data$type1)/sum(data$Nt)
# prop2 = sum(data$type2)/sum(data$Nt)
# prop3 = sum(data$type3)/sum(data$Nt)
# 
# c(prop0,prop1,prop2,prop3)
# 
# # SUBSET OF ALL THE YEARS
# y2007 = subset(data, data$y == "2007")
# y2008 = subset(data, data$y == "2008")
# y2009 = subset(data, data$y == "2009")
# y2010 = subset(data, data$y == "2010")
# y2011 = subset(data, data$y == "2011")
# y2012 = subset(data, data$y == "2012")
# y2013 = subset(data, data$y == "2013")
# y2014 = subset(data, data$y == "2014")
# y2015 = subset(data, data$y == "2015")
# y2016 = subset(data, data$y == "2016")
# y2017 = subset(data, data$y == "2017")
# y2018 = subset(data, data$y == "2018")
# 
# # PROPORTION FOR EACH YEAR
# prop0_y2007 = sum(y2007$type0)/sum(y2007$Nt)
# prop1_y2007 = sum(y2007$type1)/sum(y2007$Nt)
# prop2_y2007 = sum(y2007$type2)/sum(y2007$Nt)
# prop3_y2007 = sum(y2007$type3)/sum(y2007$Nt)
# c(prop0_y2007,prop1_y2007,prop2_y2007,prop3_y2007)
# 
# prop0_y2008 = sum(y2008$type0)/sum(y2008$Nt)
# prop1_y2008 = sum(y2008$type1)/sum(y2008$Nt)
# prop2_y2008 = sum(y2008$type2)/sum(y2008$Nt)
# prop3_y2008 = sum(y2008$type3)/sum(y2008$Nt)
# c(prop0_y2008,prop1_y2008,prop2_y2008,prop3_y2008)
# 
# prop0_y2009 = sum(y2009$type0)/sum(y2009$Nt)
# prop1_y2009 = sum(y2009$type1)/sum(y2009$Nt)
# prop2_y2009 = sum(y2009$type2)/sum(y2009$Nt)
# prop3_y2009 = sum(y2009$type3)/sum(y2009$Nt)
# c(prop0_y2009,prop1_y2009,prop2_y2009,prop3_y2009)
# 
# prop0_y2010 = sum(y2010$type0)/sum(y2010$Nt)
# prop1_y2010 = sum(y2010$type1)/sum(y2010$Nt)
# prop2_y2010 = sum(y2010$type2)/sum(y2010$Nt)
# prop3_y2010 = sum(y2010$type3)/sum(y2010$Nt)
# c(prop0_y2010,prop1_y2010,prop2_y2010,prop3_y2010)
# 
# prop0_y2011 = sum(y2011$type0)/sum(y2011$Nt)
# prop1_y2011 = sum(y2011$type1)/sum(y2011$Nt)
# prop2_y2011 = sum(y2011$type2)/sum(y2011$Nt)
# prop3_y2011 = sum(y2011$type3)/sum(y2011$Nt)
# c(prop0_y2011,prop1_y2011,prop2_y2011,prop3_y2011)
# 
# prop0_y2012 = sum(y2012$type0)/sum(y2012$Nt)
# prop1_y2012 = sum(y2012$type1)/sum(y2012$Nt)
# prop2_y2012 = sum(y2012$type2)/sum(y2012$Nt)
# prop3_y2012 = sum(y2012$type3)/sum(y2012$Nt)
# c(prop0_y2012,prop1_y2012,prop2_y2012,prop3_y2012)
# 
# prop0_y2013 = sum(y2013$type0)/sum(y2013$Nt)
# prop1_y2013 = sum(y2013$type1)/sum(y2013$Nt)
# prop2_y2013 = sum(y2013$type2)/sum(y2013$Nt)
# prop3_y2013 = sum(y2013$type3)/sum(y2013$Nt)
# c(prop0_y2013,prop1_y2013,prop2_y2013,prop3_y2013)
# 
# prop0_y2014 = sum(y2014$type0)/sum(y2014$Nt)
# prop1_y2014 = sum(y2014$type1)/sum(y2014$Nt)
# prop2_y2014 = sum(y2014$type2)/sum(y2014$Nt)
# prop3_y2014 = sum(y2014$type3)/sum(y2014$Nt)
# c(prop0_y2014,prop1_y2014,prop2_y2014,prop3_y2014)
# 
# prop0_y2015 = sum(y2015$type0)/sum(y2015$Nt)
# prop1_y2015 = sum(y2015$type1)/sum(y2015$Nt)
# prop2_y2015 = sum(y2015$type2)/sum(y2015$Nt)
# prop3_y2015 = sum(y2015$type3)/sum(y2015$Nt)
# c(prop0_y2015,prop1_y2015,prop2_y2015,prop3_y2015)
# 
# prop0_y2016 = sum(y2016$type0)/sum(y2016$Nt)
# prop1_y2016 = sum(y2016$type1)/sum(y2016$Nt)
# prop2_y2016 = sum(y2016$type2)/sum(y2016$Nt)
# prop3_y2016 = sum(y2016$type3)/sum(y2016$Nt)
# c(prop0_y2016,prop1_y2016,prop2_y2016,prop3_y2016)
# 
# prop0_y2017 = sum(y2017$type0)/sum(y2017$Nt)
# prop1_y2017 = sum(y2017$type1)/sum(y2017$Nt)
# prop2_y2017 = sum(y2017$type2)/sum(y2017$Nt)
# prop3_y2017 = sum(y2017$type3)/sum(y2017$Nt)
# c(prop0_y2017,prop1_y2017,prop2_y2017,prop3_y2017)
# 
# prop0_y2018 = sum(y2018$type0)/sum(y2018$Nt)
# prop1_y2018 = sum(y2018$type1)/sum(y2018$Nt)
# prop2_y2018 = sum(y2018$type2)/sum(y2018$Nt)
# prop3_y2018 = sum(y2018$type3)/sum(y2018$Nt)
# c(prop0_y2018,prop1_y2018,prop2_y2018,prop3_y2018)
# 
# # TOTAL NUMBER OF CALLS FOR EACH YEAR
# c(sum(y2007$Nt),sum(y2008$Nt),sum(y2009$Nt),sum(y2010$Nt))
# 
# c(sum(y2011$Nt),sum(y2012$Nt),sum(y2013$Nt),sum(y2014$Nt))
# 
# c(sum(y2015$Nt),sum(y2016$Nt),sum(y2017$Nt),sum(y2018$Nt))
# 
# # CORRELATION
# correlation = data[,c(1,2,3,4,17,16,15)]
# library(corrplot)
# M<-cor(correlation)
# corrplot(M, method="number")

library(forecast)
# Define the time series object for stores
# tsstores = ts(data$type0,start=c(2007,9,1),frequency = 365)
# plot(tsstores, main = "Advance retail sales stores", ylab = "Millions of dollars", col = "darkred", lwd = 0.1, cex.main = 1.5)
```

```{r}
library(base)
class(data$d)
             
data$date = paste0(data$d,sep="/",data$m,sep="/", data$y)
data$date = as.Date(data$date,format="%d/%m/%Y") 

p1 <- ggplot(data, aes(x=date, y=type0)) +
  geom_line(colour="#4fa8e0")+scale_x_date(date_labels = "%Y %b") + theme_bw()
p2 <- ggplot(data, aes(x=date, y=type1)) +
  geom_line(colour="#6c8bab")+scale_x_date(date_labels = "%Y %b") + theme_bw()
p3 <- ggplot(data, aes(x=date, y=type2)) +
  geom_line(colour="#72b7e3")+scale_x_date(date_labels = "%Y %b") + theme_bw()
p4 <- ggplot(data, aes(x=date, y=type3)) +
  geom_line(colour="#597d94")+scale_x_date(date_labels = "%Y %b") + theme_bw()
ggarrange(p1,p2,p3,p4,ncol=1)
```


## CODE

```{r}
X_t = data[-4079, c(1,2,3,4)]
X_w = data[-1, c(9,10,11,12,13,14,17)]
X = cbind(X_t, X_w)

rm(X_t)
rm(X_w)

library(rstan)
rstan_options(auto_write = TRUE)
#Sys.setenv(LOCAL_CPPFLAGS = '-march=native -mtune=native')
#options(mc.cores = parallel::detectCores())
```

```{r}
mlogit_model = "
data {
  int K; // 4 types of calls
  int t; // cuantos dias predecimos
  int D; // cuantos predictors
  int y[t,K]; // para cada día un vector con resultados
  matrix[t, D] x;
}
parameters {
  matrix[D, K] beta;
  real alpha;
}
model {
  matrix[t, K] x_beta = x * beta;

  to_vector(beta) ~ normal(0, 0.1);
  
  alpha ~ normal(0,0.1);

  for (i in 1:t)
    y[i,K] ~ categorical_logit(alpha + x_beta[i]');
}"
```

We do the fit by training the model with 4078 observations and we obtain the following results for the betas and alpha.

```{r, results="hide"}
#fit = stan(model_code=mlogit_model, data=list(y = data[2:4079,1:4], t=4078, K=4, D=11, x = X[seq(4078),]), iter=5000, chains = 1)
```
```{r}
#print(fit)
#saveRDS(fit, "fit_desde_obs_2.rds")
```

# FIT1

```{r}
leyendo_datos <- readRDS("fit1.rds")

df_of_draws <- as.data.frame(leyendo_datos)
print(colnames(leyendo_datos))

sets_of_betas = split.default(df_of_draws, rep(1:4, each = 11))

observaciones = data[,-c(5,6,7,8,15,16,18)] 

sets_of_betas

alpha = mean(sets_of_betas$'1'[,12])
beta1 = sets_of_betas$'1'[,-c(12,13)]
betas1 = colMeans(beta1)
beta2 = sets_of_betas$'2'
betas2 = colMeans(beta2)
beta3 = sets_of_betas$'3'
betas3 = colMeans(beta3)
beta4 = sets_of_betas$'4'
betas4 = colMeans(beta4)
x_beta = as.matrix(cbind(betas1,betas2,betas3,betas4))
x_beta
library(xtable)
bmatrix(x_beta)
```

```{r} 
type=c(1,2,3,4) 
k=4078
dd=matrix(0,nrow=k,ncol=length(type))
  for (j in 1:k){ 
    for (i in 1:4){
     dd[j,i] = as.matrix(X[j,])%*%x_beta[,i]+alpha
  } 
} 
p = exp(dd)/(1+exp(dd))  
props = p 
for (j in 1:k){
  props[j,] = p[j,]/sum(p[j,])
} 
``` 

```{r}
# Intervals
k=4078
gammas=list()
gamma_k=vector
for (i in 1:k){
 gamma_k = qgamma(c(0.025,0.975), sum(data$Nt[seq(i)]), i)
 gammas[[i]] = gamma_k
}

# Posterior mean
posterior_means = list()
posterior_mean_k = numeric(0)
for (i in 1:k){
  posterior_mean_k = (sum(data$Nt[seq(i)])+0.5)/i
  posterior_means[[i]] = posterior_mean_k
}

# Total number of calls each day
Nts = list()
Nt_k = numeric(0)
for (i in 1:k){
  Nt_k = round(mean(rpois(1000,posterior_means[[i]])),0)
  Nts[[i]] = Nt_k
}
```

```{r}
k=4078#number of observations
i=1000 #number of simulations

# conteos = rmultinom(i,N[1:k], props[1:k,])

conteos=list()
conteo_i = numeric(0)
for (j in 1:k){
  conteo_i=rmultinom(i,Nts[[j]],props[j,])
  conteos[[j]] <- conteo_i
}
# round(mean(conteos[[100]][1,]))

# Obtenemos los datos de la lista de conteos para cada dia

vector1 = c() 
vector2 = c() 
vector3 = c() 
vector4 = c() 
for (i in 1:4078){
  vector1[i]=round(mean(conteos[[i]][1,]))
  vector2[i]=round(mean(conteos[[i]][2,]))
  vector3[i]=round(mean(conteos[[i]][3,]))
  vector4[i]=round(mean(conteos[[i]][4,]))
  
}

# Base de datos de resultados

results = data[-1,]
results$type0 = vector1
results$type1 = vector2
results$type2 = vector3
results$type3 = vector4
results$Nt = rowSums(results[,1:4])

results_1 = results

mae(results_1$type0, data[-1,]$type0)
mae(results_1$type1, data[-1,]$type1)
mae(results_1$type2, data[-1,]$type2)
mae(results_1$type3, data[-1,]$type3)
mae(results_1$Nt, data[-1,]$Nt)
```
# FIT100

Cogiendo solo 100 dias.

```{r, results="hide"}
#fit3 = stan(model_code=mlogit_model, data=list(y = data[1:100,1:4], t=100, K=4, D=11, x = X[seq(100),]), iter=5000, chains = 1)
```

```{r}
# print(fit3)
# fit3 = saveRDS(fit3, "fit_100.rds")
```

```{r}
leyendo_datos <- readRDS("fit_100.rds")
print(leyendo_datos)
df_of_draws <- as.data.frame(leyendo_datos)
print(colnames(leyendo_datos))

sets_of_betas = split.default(df_of_draws, rep(1:4, each = 11))

observaciones = data[,-c(5,6,7,8,15,16,18)] 

sets_of_betas

alpha = mean(sets_of_betas$'1'[,12])
beta1 = sets_of_betas$'1'[,-c(12,13)]
betas1 = colMeans(beta1)
beta2 = sets_of_betas$'2'
betas2 = colMeans(beta2)
beta3 = sets_of_betas$'3'
betas3 = colMeans(beta3)
beta4 = sets_of_betas$'4'
betas4 = colMeans(beta4)
x_beta = as.matrix(cbind(betas1,betas2,betas3,betas4))
bmatrix(x_beta)
```

```{r} 
type=c(1,2,3,4) 
k=4078
dd=matrix(0,nrow=k,ncol=length(type))
  for (j in 1:k){ 
    for (i in 1:4){
     dd[j,i] = as.matrix(X[j,])%*%x_beta[,i]+alpha
  } 
} 
p = exp(dd)/(1+exp(dd))  
props = p 
for (j in 1:k){
  props[j,] = p[j,]/sum(p[j,])
} 
``` 

```{r}
# Intervals
k=4078
gammas=list()
gamma_k=vector
for (i in 1:k){
 gamma_k = qgamma(c(0.025,0.975), sum(data$Nt[seq(i)]), i)
 gammas[[i]] = gamma_k
}

# Posterior mean
posterior_means = list()
posterior_mean_k = numeric(0)
for (i in 1:k){
  posterior_mean_k = (sum(data$Nt[seq(i)])+0.5)/i
  posterior_means[[i]] = posterior_mean_k
}

# Total number of calls each day
Nts = list()
Nt_k = numeric(0)
for (i in 1:k){
  Nt_k = round(mean(rpois(1000,posterior_means[[i]])),0)
  Nts[[i]] = Nt_k
}
```

```{r}
k=4078#number of observations
i=1000 #number of simulations

# conteos = rmultinom(i,N[1:k], props[1:k,])

conteos=list()
conteo_i = numeric(0)
for (j in 1:k){
  conteo_i=rmultinom(i,Nts[[j]],props[j,])
  conteos[[j]] <- conteo_i
}
# round(mean(conteos[[100]][1,]))

# Obtenemos los datos de la lista de conteos para cada dia

vector1 = c() 
vector2 = c() 
vector3 = c() 
vector4 = c() 
for (i in 1:4078){
  vector1[i]=round(mean(conteos[[i]][1,]))
  vector2[i]=round(mean(conteos[[i]][2,]))
  vector3[i]=round(mean(conteos[[i]][3,]))
  vector4[i]=round(mean(conteos[[i]][4,]))
  
}

# Base de datos de resultados

results = data[-1,]
results$type0 = vector1
results$type1 = vector2
results$type2 = vector3
results$type3 = vector4
results$Nt = rowSums(results[,1:4])

results_100 = results

mae(results_100$type0, data[-1,]$type0)
mae(results_100$type1, data[-1,]$type1)
mae(results_100$type2, data[-1,]$type2)
mae(results_100$type3, data[-1,]$type3)
mae(results_100$Nt, data[-1,]$Nt)
```

# FIT 1000

Cogiendo 1000 solo por curiosidad.

```{r, results="hide"}
#fit2 = stan(model_code=mlogit_model, data=list(y = data[1:1000,1:4], t=1000, K=4, D=11, x = X[seq(1000),]), iter=5000, chains = 1)
```

```{r}
# print(fit2)
# fit2 = saveRDS(fit2, "fit_1000.rds")
```

```{r}
leyendo_datos <- readRDS("fit_1000.rds")

df_of_draws <- as.data.frame(leyendo_datos)
print(colnames(leyendo_datos))

sets_of_betas = split.default(df_of_draws, rep(1:4, each = 11))

observaciones = data[,-c(5,6,7,8,15,16,18)] 

sets_of_betas

alpha = mean(sets_of_betas$'1'[,12])
beta1 = sets_of_betas$'1'[,-c(12,13)]
betas1 = colMeans(beta1)
beta2 = sets_of_betas$'2'
betas2 = colMeans(beta2)
beta3 = sets_of_betas$'3'
betas3 = colMeans(beta3)
beta4 = sets_of_betas$'4'
betas4 = colMeans(beta4)
x_beta = as.matrix(cbind(betas1,betas2,betas3,betas4))
bmatrix(x_beta)
```

```{r} 
type=c(1,2,3,4) 
k=4078
dd=matrix(0,nrow=k,ncol=length(type))
  for (j in 1:k){ 
    for (i in 1:4){
     dd[j,i] = as.matrix(X[j,])%*%x_beta[,i]+alpha
  } 
} 
p = exp(dd)/(1+exp(dd))  
props = p 
for (j in 1:k){
  props[j,] = p[j,]/sum(p[j,])
} 
``` 

```{r}
# Intervals
k=4078
gammas=list()
gamma_k=vector
for (i in 1:k){
 gamma_k = qgamma(c(0.025,0.975), sum(data$Nt[seq(i)]), i)
 gammas[[i]] = gamma_k
}

# Posterior mean
posterior_means = list()
posterior_mean_k = numeric(0)
for (i in 1:k){
  posterior_mean_k = (sum(data$Nt[seq(i)])+0.5)/i
  posterior_means[[i]] = posterior_mean_k
}

# Total number of calls each day
Nts = list()
Nt_k = numeric(0)
for (i in 1:k){
  Nt_k = round(mean(rpois(1000,posterior_means[[i]])),0)
  Nts[[i]] = Nt_k
}
```

```{r}
k=4078#number of observations
i=1000 #number of simulations

# conteos = rmultinom(i,N[1:k], props[1:k,])

conteos=list()
conteo_i = numeric(0)
for (j in 1:k){
  conteo_i=rmultinom(i,Nts[[j]],props[j,])
  conteos[[j]] <- conteo_i
}
# round(mean(conteos[[100]][1,]))

# Obtenemos los datos de la lista de conteos para cada dia

vector1 = c() 
vector2 = c() 
vector3 = c() 
vector4 = c() 
for (i in 1:4078){
  vector1[i]=round(mean(conteos[[i]][1,]))
  vector2[i]=round(mean(conteos[[i]][2,]))
  vector3[i]=round(mean(conteos[[i]][3,]))
  vector4[i]=round(mean(conteos[[i]][4,]))
  
}

# Base de datos de resultados

results = data[-1,]
results$type0 = vector1
results$type1 = vector2
results$type2 = vector3
results$type3 = vector4
results$Nt = rowSums(results[,1:4])

results_1000 = results

mae(results_1000$type0, data[-1,]$type0)
mae(results_1000$type1, data[-1,]$type1)
mae(results_1000$type2, data[-1,]$type2)
mae(results_1000$type3, data[-1,]$type3)
mae(results_1000$Nt, data[-1,]$Nt)

```


# FIT HASTA 2016

Cogiendo hasta el año 2016.

```{r, results="hide"}
# fit4 = stan(model_code=mlogit_model, data=list(y = data[1:3044,1:4], t=3044, K=4, D=11, x = X[seq(3044),]), iter=5000, chains = 1)
```

```{r}
# print(fit4)
# fit4 = saveRDS(fit4, "fit_hasta_2016.rds")
```

```{r}
leyendo_datos <- readRDS("fit_hasta_2016.rds")

df_of_draws <- as.data.frame(leyendo_datos)
print(colnames(leyendo_datos))

sets_of_betas = split.default(df_of_draws, rep(1:4, each = 11))

observaciones = data[,-c(5,6,7,8,15,16,18)] 

sets_of_betas

alpha = mean(sets_of_betas$'1'[,12])
beta1 = sets_of_betas$'1'[,-c(12,13)]
betas1 = colMeans(beta1)
beta2 = sets_of_betas$'2'
betas2 = colMeans(beta2)
beta3 = sets_of_betas$'3'
betas3 = colMeans(beta3)
beta4 = sets_of_betas$'4'
betas4 = colMeans(beta4)
x_beta = as.matrix(cbind(betas1,betas2,betas3,betas4))
bmatrix(x_beta)
```

```{r} 
type=c(1,2,3,4) 
k=4078
dd=matrix(0,nrow=k,ncol=length(type))
  for (j in 1:k){ 
    for (i in 1:4){
     dd[j,i] = as.matrix(X[j,])%*%x_beta[,i]+alpha
  } 
} 
p = exp(dd)/(1+exp(dd))  
props = p 
for (j in 1:k){
  props[j,] = p[j,]/sum(p[j,])
} 
``` 

```{r}
# Intervals
k=4078
gammas=list()
gamma_k=vector
for (i in 1:k){
 gamma_k = qgamma(c(0.025,0.975), sum(data$Nt[seq(i)]), i)
 gammas[[i]] = gamma_k
}

# Posterior mean
posterior_means = list()
posterior_mean_k = numeric(0)
for (i in 1:k){
  posterior_mean_k = (sum(data$Nt[seq(i)])+0.5)/i
  posterior_means[[i]] = posterior_mean_k
}

# Total number of calls each day
Nts = list()
Nt_k = numeric(0)
for (i in 1:k){
  Nt_k = round(mean(rpois(1000,posterior_means[[i]])),0)
  Nts[[i]] = Nt_k
}
```

```{r}
k=4078#number of observations
i=1000 #number of simulations

# conteos = rmultinom(i,N[1:k], props[1:k,])

conteos=list()
conteo_i = numeric(0)
for (j in 1:k){
  conteo_i=rmultinom(i,Nts[[j]],props[j,])
  conteos[[j]] <- conteo_i
}
# round(mean(conteos[[100]][1,]))

# Obtenemos los datos de la lista de conteos para cada dia

vector1 = c() 
vector2 = c() 
vector3 = c() 
vector4 = c() 
for (i in 1:4078){
  vector1[i]=round(mean(conteos[[i]][1,]))
  vector2[i]=round(mean(conteos[[i]][2,]))
  vector3[i]=round(mean(conteos[[i]][3,]))
  vector4[i]=round(mean(conteos[[i]][4,]))
  
}

# Base de datos de resultados

results = data[-1,]
results$type0 = vector1
results$type1 = vector2
results$type2 = vector3
results$type3 = vector4
results$Nt = rowSums(results[,1:4])

results_hasta_2016 = results

mae(results_hasta_2016$type0, data[-1,]$type0)
mae(results_hasta_2016$type1, data[-1,]$type1)
mae(results_hasta_2016$type2, data[-1,]$type2)
mae(results_hasta_2016$type3, data[-1,]$type3)
mae(results_hasta_2016$Nt, data[-1,]$Nt)
```

# FIT DESDE 2016

Cogiendo desde el año 2016. (falta este)

```{r, results="hide"}
#fit5 = stan(model_code=mlogit_model, data=list(y = data[3044:4078,1:4], t=1035, K=4, D=11, x = X[-seq(3043),]), iter=5000, chains = 1)
```

```{r}
# print(fit5)
#saveRDS(fit5, "fit_desde_2016.rds")
```

```{r}
leyendo_datos <- readRDS("fit_desde_2016.rds")

df_of_draws <- as.data.frame(leyendo_datos)
print(colnames(leyendo_datos))

sets_of_betas = split.default(df_of_draws, rep(1:4, each = 11))

observaciones = data[,-c(5,6,7,8,15,16,18)] 

sets_of_betas

alpha = mean(sets_of_betas$'1'[,12])
beta1 = sets_of_betas$'1'[,-c(12,13)]
betas1 = colMeans(beta1)
beta2 = sets_of_betas$'2'
betas2 = colMeans(beta2)
beta3 = sets_of_betas$'3'
betas3 = colMeans(beta3)
beta4 = sets_of_betas$'4'
betas4 = colMeans(beta4)
x_beta = as.matrix(cbind(betas1,betas2,betas3,betas4))
bmatrix(x_beta)
```

```{r} 
type=c(1,2,3,4) 
k=4078
dd=matrix(0,nrow=k,ncol=length(type))
  for (j in 1:k){ 
    for (i in 1:4){
     dd[j,i] = as.matrix(X[j,])%*%x_beta[,i]+alpha
  } 
} 
p = exp(dd)/(1+exp(dd))  
props = p 
for (j in 1:k){
  props[j,] = p[j,]/sum(p[j,])
} 
``` 

```{r}
# Intervals
k=4078
gammas=list()
gamma_k=vector
for (i in 1:k){
 gamma_k = qgamma(c(0.025,0.975), sum(data$Nt[seq(i)]), i)
 gammas[[i]] = gamma_k
}

# Posterior mean
posterior_means = list()
posterior_mean_k = numeric(0)
for (i in 1:k){
  posterior_mean_k = (sum(data$Nt[seq(i)])+0.5)/i
  posterior_means[[i]] = posterior_mean_k
}

# Total number of calls each day
Nts = list()
Nt_k = numeric(0)
for (i in 1:k){
  Nt_k = round(mean(rpois(100,posterior_means[[i]])),0)
  Nts[[i]] = Nt_k
}
```

```{r}
k=4078#number of observations
i=200 #number of simulations

# conteos = rmultinom(i,N[1:k], props[1:k,])

conteos=list()
conteo_i = numeric(0)
for (j in 1:k){
  conteo_i=rmultinom(i,Nts[[j]],props[j,])
  conteos[[j]] <- conteo_i
}
# round(mean(conteos[[100]][1,]))

# Obtenemos los datos de la lista de conteos para cada dia

vector1 = c() 
vector2 = c() 
vector3 = c() 
vector4 = c() 
for (i in 1:4078){
  vector1[i]=round(mean(conteos[[i]][1,]))
  vector2[i]=round(mean(conteos[[i]][2,]))
  vector3[i]=round(mean(conteos[[i]][3,]))
  vector4[i]=round(mean(conteos[[i]][4,]))
  
}

# Base de datos de resultados

results = data[-1,]
results$type0 = vector1
results$type1 = vector2
results$type2 = vector3
results$type3 = vector4
results$Nt = rowSums(results[,1:4])

results_desde_2016 = results

mae(results_desde_2016$type0, data[-1,]$type0)
mae(results_desde_2016$type1, data[-1,]$type1)
mae(results_desde_2016$type2, data[-1,]$type2)
mae(results_desde_2016$type3, data[-1,]$type3)
mae(results_desde_2016$Nt, data[-1,]$Nt)
```

# FIT PRIOR 0.05

```{r}
leyendo_datos <- readRDS("fit_0.05.rds")

df_of_draws <- as.data.frame(leyendo_datos)
print(colnames(leyendo_datos))

sets_of_betas = split.default(df_of_draws, rep(1:4, each = 11))

observaciones = data[,-c(5,6,7,8,15,16,18)] 

sets_of_betas

alpha = mean(sets_of_betas$'1'[,12])
beta1 = sets_of_betas$'1'[,-c(12,13)]
betas1 = colMeans(beta1)
beta2 = sets_of_betas$'2'
betas2 = colMeans(beta2)
beta3 = sets_of_betas$'3'
betas3 = colMeans(beta3)
beta4 = sets_of_betas$'4'
betas4 = colMeans(beta4)
x_beta = as.matrix(cbind(betas1,betas2,betas3,betas4))
bmatrix(x_beta)
```

```{r} 
type=c(1,2,3,4) 
k=4078
dd=matrix(0,nrow=k,ncol=length(type))
  for (j in 1:k){ 
    for (i in 1:4){
     dd[j,i] = as.matrix(X[j,])%*%x_beta[,i]+alpha
  } 
} 
p = exp(dd)/(1+exp(dd))  
props = p 
for (j in 1:k){
  props[j,] = p[j,]/sum(p[j,])
} 
``` 

```{r}
# Intervals
k=4078
gammas=list()
gamma_k=vector
for (i in 1:k){
 gamma_k = qgamma(c(0.025,0.975), sum(data$Nt[seq(i)]), i)
 gammas[[i]] = gamma_k
}

# Posterior mean
posterior_means = list()
posterior_mean_k = numeric(0)
for (i in 1:k){
  posterior_mean_k = (sum(data$Nt[seq(i)])+0.5)/i
  posterior_means[[i]] = posterior_mean_k
}

# Total number of calls each day
Nts = list()
Nt_k = numeric(0)
for (i in 1:k){
  Nt_k = round(mean(rpois(1000,posterior_means[[i]])),0)
  Nts[[i]] = Nt_k
}
```

```{r}
k=4078#number of observations
i=1000 #number of simulations

# conteos = rmultinom(i,N[1:k], props[1:k,])

conteos=list()
conteo_i = numeric(0)
for (j in 1:k){
  conteo_i=rmultinom(i,Nts[[j]],props[j,])
  conteos[[j]] <- conteo_i
}
# round(mean(conteos[[100]][1,]))

# Obtenemos los datos de la lista de conteos para cada dia

vector1 = c() 
vector2 = c() 
vector3 = c() 
vector4 = c() 
for (i in 1:4078){
  vector1[i]=round(mean(conteos[[i]][1,]))
  vector2[i]=round(mean(conteos[[i]][2,]))
  vector3[i]=round(mean(conteos[[i]][3,]))
  vector4[i]=round(mean(conteos[[i]][4,]))
  
}

# Base de datos de resultados

results = data[-1,]
results$type0 = vector1
results$type1 = vector2
results$type2 = vector3
results$type3 = vector4
results$Nt = rowSums(results[,1:4])

results_beta_0.05 = results

rmse(results_beta_0.05$type0, data$type0)
rmse(results_beta_0.05$type1, data$type1)
rmse(results_beta_0.05$type2, data$type2)
rmse(results_beta_0.05$type3, data$type3)
rmse(results_beta_0.05$Nt, data$Nt)
```

# GRAFICO

Para plotear en función del tiempo cada grupo de resultados.

```{r}
results$date = paste0(results$d,sep="/",results$m,sep="/", results$y)
results$date = as.Date(results$date,format="%d/%m/%Y") 

p1 <- ggplot(results, aes(x=date, y=type0)) +
  geom_line(colour="#4fa8e0",alpha=1)+
  geom_line(data = data, aes(x = date, y = type0), color = "red",alpha=0.45) + scale_x_date(date_labels = "%Y %b") + theme_bw()
p2 <- ggplot(results, aes(x=date, y=type1)) +
  geom_line(colour="#6c8bab",alpha=1)+
  geom_line(data = data, aes(x = date, y = type1), color = "red",alpha=0.45) +
  scale_x_date(date_labels = "%Y %b") + theme_bw()
p3 <- ggplot(results, aes(x=date, y=type2)) +
  geom_line(colour="#72b7e3",alpha=1)+
  geom_line(data = data, aes(x = date, y = type2), color = "red",alpha=0.55)+ 
  scale_x_date(date_labels = "%Y %b") + theme_bw()
p4 <- ggplot(results, aes(x=date, y=type3)) +
  geom_line(colour="#597d94",alpha=1)+
  geom_line(data = data, aes(x = date, y = type3), color = "red",alpha=0.55) +
  scale_x_date(date_labels = "%Y %b") + theme_bw()
ggarrange(p1,p2,p3,p4,ncol=1,)

```





